\LARGE \bf Multi-Arm Bandit Models for 2D Grasp Planning with Uncertainty [v6 Feb 18, 2015 ]

### 2015-03-05 paper.tex
added stuff

\title{\LARGE \bf
Multi-Arm Bandit Models for 2D Grasp Planning with Uncertainty  [v5 Feb 18, 2015 ] }

@@

%We chose of the line of action model because perturbations to a surface resulting from shape uncertainty lead to changesa in the location of contact with a surface, and the line of action allows us to compute these new locations.
\todo{The next section was crossed out in your notes, I'm still not clear whats wrong with it. Can you elaborate more?}
Given a grasp plan and a deterministic shape, we define the {\it contact points} as the spatial locations at which the jaws come into contact with the object when following along the grasp axis, $\bc_1, \bc_2 \in \mathbb{R}^2$.
We also refer to the unit outward pointing surface normals at the contact points as $\bn_1 \bn_2 \in \mathbb{R}^d$, the object center of mass as $\bz \in \mathbb{R}^d$ and the friction coefficient as $\mu$.
Together these form the set of grasp parameters $g = (\bc_1,\bc_2, \bn_1, \bn_2, \bz,\mu)$ that enable us to evaluate the forces and torques that a given grasp can apply to an object \cite{ferrari1992}.

@@

 .
\section{Simulation Experiments}
We used the Brown Vision Lab 2D dataset \cite{brown}, the same used in \cite{christopoulos2007handling}.Examples of the images can be seen in \ref{fig:shape_samples}.  We down sampled the image by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values. The parameters of the GPIS were selected using maximum likelihood on a held-out set of validation shapes. For illustrative purposes, the noise of the motion, position and friction coefficient was set to the following variances $\sigma_{mot} = 0.2$ rads, $\sigma_{mu} = 0.4$, $\sigma_{rot} = 0.3$ rads and $\sigma_{trans} = 3$ grid cells.
We us the GPIS-Blur visualization technique \cite{mahler2015gp}.
We performed experiments for the case of two hard contacts in 2-D. We drew random grasp plans $\Gamma$ by sampling the angle of grasp axis around a circle with radius $\sqrt{2} M$, where $M$ is the dimension of the workspace, and then sampling the circle's origin.

\subsection{Multi-Armed Bandit Experiments}
For our experiments we look at selecting the best grasp out of a size of $|G| = 1000$. We initialize all algorithms by sampling each grasp 1 time. We draw samples from our graphical model using the technique described in Sec.  \ref{sec:grasp_sample}. In Fig. \ref{fig:grasp_quality}, we plotted the probability of force closure, $P_F$, of the grasp chosen vs. stopping time $T_s$ averaged over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and compare the four different methods (Thompson, Gittins, Adaptive Sampling \cite{kehoe2012toward} and Monte-Carlo Integration). We set the discount factor $\gamma =0.98$ for Gittins because that was the highest we could compute the indices for, since it scales exponentially in computation. The adaptive sampling method of Kehoe et al. prunes grasps every 1000 iterations based on lowest sample mean and removes 10$\%$ of the current grasp set.  To illustrate the difference in grasp quality returned at a stopping time of $T = 9000$,  we show the grasps selected for three randomly selected objects for all methods listed in Fig. \ref{fig:shape_samples}. Interestingly in Fig. \ref{fig:grasp_quality}, Gittins and Thompson select at stopping time $T_s$ on average higher quality grasps than Monte-Carlo integration and the method listed in Kehoe et al \cite{kehoe2012toward} with the same number of samples drawn .

 In Fig. \ref{fig:pulls_per_grasp}, we plot samples per grasp quality. Gittins and Thompson appear to allocate  more samples to grasps of high quality. In contrast to Monte-Carlo, which uniformly allocate grasp samples. The ability to find grasps with a higher probability of force  faster can be explain by the fact that MAB methods hone in their sampling efforts on promising grasps, for the top 10$\%$ of grasps Thompson Sampling allocates 0.29$\%$ of the total number of samples and Gittins allocates 0.28$\%$ of total samples. Monte-Carlo sampling allocates $0.01\%$ of total samples to the top 10$\%$ of grasps. The adaptive sampling method proposed by Kehoe et al. allocates 0.06$\%$  of total samples to the top 10 $\%$ of grasps.

 The MAB algorithm can also be terminated not at a fix stopping time $T_s$, but at the time when the $95\%$ confidence interval around the estimated best grasp is below a set threshold $\epsilon$. We plot the confidence intervals around the return grasp vs. the number of samples drawn in Fig. \ref{fig:confidence} for Thompson Sampling, the adaptive sampling method\cite{kehoe2012toward} and Monte-Carlo Sampling. As illustrated, the confidence interval for Thompson sampling converges at a faster rate than the other two methods. This can be explained by the fact that more samples are allocated on average to grasp returned at each iteration, which is illustrated in Fig. \ref{fig:pulls_per_grasp}.

\begin{figure}[ht!]
\centering
\includegraphics[width = 8.5cm, height = 9cm]{matlab_figures/pfc.eps}
\caption{ \footnotesize Comparison of the current average probability of force closure vs. the stopping time $T_s$.Graph is averaged over 100 shapes randomly drawn from the Brown Vision 2D Lab Dataset \cite{brown} with a set $|G|=1000$ for each shape.  We demonstrate this for Thompson, Gittins, Monte-Carlo and the approach taking in Kehoe et al \cite{kehoe2012toward}. We also demonstrate what the average probability of force closure for the approximate optimal policy. Empirically, it appears that Thompson and Gittins converge at a faster rate to the optimal solution, which is desired for an anytime algorithm  }
\vspace*{-10pt}
\label{fig:grasp_quality}
\end{figure}

@@

For translational uncertainty in pose, we varied $\sigma_{trans}$ in the range of $\lbrace 3,12, 24 \rbrace$ units (on a 40 x 40 unit workspace). As you can see in Fig. \ref{fig:rot_sens}, the performance of the bandit algorithms is effected by the change in rotation, increase noise of $\sigma_{trans} = 24$ causes the convergence to not be reached until 8763 evaluations for Thompson Sampling.

>>>>

\title{\LARGE \bf
Multi-Arm Bandit Models for 2D Grasp Planning with Uncertainty  [v6 Feb 18, 2015 ] }

@@

%We chose of the line of action model because perturbations to a surface resulting from shape uncertainty lead to changesa in the location of contact with a surface, and the line of action allows us to compute these new locations.
\todo{The next section was crossed out in your notes, I'm still not clear on whats wrong with it. Can you elaborate more?}
Given a grasp plan and a deterministic shape, we define the {\it contact points} as the spatial locations at which the jaws come into contact with the object when following along the grasp axis, $\bc_1, \bc_2 \in \mathbb{R}^2$.
We also refer to the unit outward pointing surface normals at the contact points as $\bn_1 \bn_2 \in \mathbb{R}^d$, the object center of mass as $\bz \in \mathbb{R}^d$ and the friction coefficient as $\mu$.
Together these form the set of grasp parameters $g = (\bc_1,\bc_2, \bn_1, \bn_2, \bz,\mu)$ that enable us to evaluate the forces and torques that a given grasp can apply to an object \cite{ferrari1992}.

@@

 .
\section{Simulation Experiments}
We used the Brown Vision Lab 2D dataset \cite{brown}, the same used in \cite{christopoulos2007handling}.Examples of the images can be seen in \ref{fig:shape_samples}.  We down sampled the image by a factor of 2 to create a 40 x 40 occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values. The parameters of the GPIS were selected using maximum likelihood on a held-out set of validation shapes. For illustrative purposes of noise, the noise of the motion, position and friction coefficient was set to the following variances $\sigma_{mot} = 0.2$ rads, $\sigma_{mu} = 0.4$, $\sigma_{rot} = 0.3$ rads and $\sigma_{trans} = 3$ grid cells.
We performed experiments for the case of two hard contacts in 2-D. We drew random grasp plans $\Gamma$ by sampling the angle of grasp axis around a circle with radius $\sqrt{2} M$, where $M$ is the dimension of the workspace, and then sampling the circle's origin.

\subsection{Multi-Armed Bandit Experiments}
For our experiments we look at selecting the best grasp out of a size of $|G| = 1000$. We initialize all algorithms by sampling each grasp 1 time. We draw samples from our graphical model using the technique described in Sec.  \ref{sec:grasp_sample}. In Fig. \ref{fig:grasp_quality}, we plotted the probability of force closure, $P_F$, of the grasp chosen vs. stopping time $T_s$ averaged over 100 randomly selected shapes in the Brown Vision Lab 2D dataset and compare the four different methods (Thompson, Gittins, Adaptive Sampling \cite{kehoe2012toward} and Monte-Carlo Integration). We set the discount factor $\gamma =0.98$ for Gittins because that was the highest we could compute the indices for, since it scales exponentially in computation. The adaptive sampling method of Kehoe et al. prunes grasps every 1000 iterations based on lowest sample mean and removes 10$\%$ of the current grasp set.  \todo{THis might still be vague} For illustrative purposes we select a stopping time $T_s=1000$, which is only 10 samples per grasp on average and show the grasps selected for three randomly selected objects for the tried methods in Fig. \ref{fig:shape_samples}. Interestingly in Fig. \ref{fig:grasp_quality}, Gittins and Thompson select a stopping time $T_s$ on average higher quality grasps than Monte-Carlo integration and the method listed in Kehoe et al \cite{kehoe2012toward} with the same number of samples drawn .

 In Fig. \ref{fig:pulls_per_grasp}, we plot samples per grasp quality. Gittins and Thompson appear to allocate  more samples to grasps of high quality. In contrast to Monte-Carlo, which uniformly allocate grasp samples. The ability to find grasps with a higher probability of force  faster can be explain by the fact that MAB methods hone in their sampling efforts on promising grasps, for the top 10$\%$ of grasps Thompson Sampling allocates 0.29$\%$ of the total number of samples and Gittins allocates 0.28$\%$ of total samples. Monte-Carlo sampling and the adaptive sampling method allocate $0.01\%$  and $0.06\%$ of total samples, respectively.

 The MAB algorithm can also be terminated not at a fix stopping time $T_s$, but at the time when the $95\%$ confidence interval, Eq. \ref{eq:confidence}, around the returned grasp is below a set threshold $\epsilon$. We plot the confidence intervals around the return grasp vs. the number of samples drawn in Fig. \ref{fig:confidence} for Thompson Sampling, the adaptive sampling method\cite{kehoe2012toward} and Monte-Carlo Sampling. \todo{Still thinking of a way to quantify this} As illustrated, the confidence interval for Thompson sampling converges at a faster rate than the other two methods. This can be explained by the fact that in our experiments the MAB algorithms allocate more samples on average to grasp returned at each iteration, which is illustrated in Fig. \ref{fig:pulls_per_grasp}.

\begin{figure}[ht!]
\centering
\includegraphics[width = 8.5cm, height = 9cm]{matlab_figures/pfc.eps}
\caption{ \footnotesize Comparison of the current average probability of force closure vs. the stopping time $T_s$.Graph is averaged over 100 shapes randomly drawn from the Brown Vision 2D Lab Dataset \cite{brown} with a set $|G|=1000$ for each shape.  We demonstrate this for Thompson, Gittins, Monte-Carlo and the Adaptive Sampling approach \cite{kehoe2012toward}. We also demonstrate what the average probability of force closure for the approximate optimal policy. Empirically, it appears that Thompson and Gittins converge at a faster rate to the optimal solution, which is desired for an anytime algorithm  }
\vspace*{-10pt}
\label{fig:grasp_quality}
\end{figure}

@@

For translational uncertainty in pose, we varied $\sigma_{trans}$ in the range of $\lbrace 3,12, 24 \rbrace$ units (on a 40 x 40 unit workspace). As you can see in Table 1, the performance of the bandit algorithms is effected by the change in rotation, increase noise of $\sigma_{trans} = 24$ causes the convergence to not be reached until 8763 evaluations for Thompson Sampling.
